---
title: "Minimal Sample Analysis"
output: html_notebook
---

```{r, echo=FALSE}
# Start-up
# Packages ...
suppressPackageStartupMessages(require(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(require(magrittr, quietly = TRUE))

"%nin%" = Negate("%in%")

# Data ....
load(file = "../analysis-files/snapshot_integrated-datasets_min-sample.Rdata") # 500 samples per scenario run

```

```{r}
rm(list = setdiff(ls(), c("deg"))) # keep only objects relevant for analysis
```

### Objective

Estimate the minimum samples necessary for first-round sensitivity analysis.

-   Round 1: Applicable for all scenarios. Determine which scenarios are above / below **Sufficient** and **Deficient** thresholds as defined in "model_sensitivity.R" script; corresponding parameters are [param.perf_thld_high] and [param.perf_thld_low], with default values of 0.90 and 0.30.\
    \
    Should be minimal sample test, scenarios that don't fall into either of these groups should be re-tested at a high sample size to determine model performance aligns with management expecations.

-   Round 2: Applicable for only scenarios that score between sufficient and deficient thresholds, with an initial outcome status of "To Be Determined". High sample re-testing to model and evaluate model performance.

### Analysis

The following summarizes scenario performance at a sample size of (n=500).

```{r, echo=FALSE}
perf_summary = deg %>% 
  group_by(scenario) %>% 
  count(true_positive_match) %>% 
  mutate(N = sum(n),
         pcnt = n/sum(n)) %>% 
  filter(true_positive_match) %>% 
  arrange(desc(pcnt)) %>% 
  select(scenario, N, pcnt) %>% 
  rename(sample_size = N, 
         match_rate = pcnt)
  
perf_summary

```

Scenarios with a 100% match rate were ignored.

```{r}

deg = deg %>%
  filter(scenario %nin% perf_summary$scenario[which(perf_summary$match_rate == 1)])

deg = deg %>% 
  select(scenario, true_positive_match)

```

Match rates were bootstrapped at various key sample sizes to visualize the relationship between sample size and known match rates.

```{r}
n_range = seq(50, 450, by = 50)
resamples = 50 # how many resamples?

dat = list()

for(j in seq_along(perf_summary$))

```

```{r}
n_samples = seq(from = 25, to = 500, by = 25)
resamples = 20

temp = deg %>% filter(scenario == "stripping")
temp2 = vector(mode = "list", length = 0)
k = 0
for(i in seq_along(n_samples)){
  
  for(j in seq_len(resamples)){
  k = k + 1
    
  temp2[[k]] = temp %>% 
  sample_n(size = n_samples[i]) %>% 
  group_by(scenario) %>% 
  count(true_positive_match) %>% 
  mutate(pcnt = n/sum(n)) %>% 
  mutate(N = n_samples[i]) %>%
  filter(true_positive_match) %>% 
  arrange(desc(pcnt))
    
  }
  
  
  
}

```

```{r}

```
